%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Laboratório de Computação Embarcada e Tecnologias Industriais (LACETI-CIN)}{Nov 2022 -- present}
{Tech Lead - DevOps Developer}{Recife-PE, Brasil}
\resumeItemListStart
\resumeItem{Implemented a data lake for 76,000 IoT devices using MQTT, Apache NiFi, MinIO (S3), Kafka, and Spark. Integrated Jupyter, MLflow, and KServe for analytics and ML. Managed infrastructure with Terraform. The system processes data in real time and in batch mode, offering scalability and flexibility.}
\resumeItem{Built a CI/CD pipeline using CircleCI and ArgoCD, reducing deployment time by 40\% and ensuring consistent and reliable releases.}
\resumeItem{Led a cross-functional team of 6 in implementing a second version of a manufacturing line execution system (MES) using React and Node.js, resulting in a 25\% performance increase.}
\resumeItemListEnd

\resumeSubheading
{Laboratório de Computação Embarcada e Tecnologias Industriais (LACETI-CIN)}{June 2021 -- Nov 2022}
{Software Engineer - Fullstack Developer}{Recife-PE, Brasil}
\resumeItemListStart
\resumeItem{Contributed to the development of a Manufacturing Execution System (MES) for a lead-acid battery production line, using a modern technology stack that included React, GraphQL, and Node.js. As part of an agile team, I developed responsive user interfaces, implemented efficient APIs and GraphQL services, and integrated real-time data from the production line.}
\resumeItem{implemented automated testing for front-end applications, achieving 90\% coverage. Using Cypress for end-to-end testing and Jest for unit testing, he developed a suite that ensured the functional integrity of the application.}
\resumeItem{Optimization of data synchronization between production line sensors and cloud systems using a caching system with Redis and Node.js. The solution reduced latency in data transmission and improved synchronization reliability.}
\resumeItemListEnd

\resumeSubheading
{Laboratório Multidisciplinar de Tecnologias Sociais (LMTS)}{May 2019 -- June 2021}
{Software Engineer - Fullstack Developer}{Garanhuns-PE, Brasil}
\resumeItemListStart
\resumeItem{Developed 'VacinaGaranhuns', a React system with Google Maps for controlling and scheduling COVID-19 vaccinations, serving 12,000 people. Implemented geolocated visualization of posts, online scheduling, and a module for home vaccination. Optimized vaccine distribution and efficiency of the municipal campaign.}
\resumeItem{Led the development of a smart irrigation system with React Native and Node.js, integrating meteorological APIs and IoT devices. Uses advanced analytics for accurate evapotranspiration calculation, resulting in 62\% reduction in water consumption for small farmers.}
\resumeItemListEnd

\resumeSubHeadingListEnd