%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\href{https://github.com/luancsl/SIA}{\textbf{Smart Irrigation API (SIA)}} $|$ \emph{Node.js, Express.js, MongoDB, Jest, Cheerio}}    {}
\resumeItemListStart
\resumeItem{Designed and implemented a RESTful API for integrating multiple climate data providers, using geographic coordinates as the main parameter.}
\resumeItem{Developed an efficient caching system that optimized performance, allowing fast access to regional climate data without the need for frequent recalculations, resulting in a significant 30\% reduction in API response time.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/luancsl/GrowApp}{\textbf{Smart irrigation application (GrowApp)}} $|$ \emph{React-Native, Google Maps, Jest, Watermelondb}}{}
\resumeItemListStart
\resumeItem{Developed a mobile application in React Native with Google Maps to optimize agricultural irrigation. The system integrates real-time evapotranspiration calculations and IoT devices, resulting in a 62\% reduction in water consumption for small rural producers.}
\resumeItem{Built a LoRa mesh network for actuator devices in remote agricultural irrigation areas, significantly expanding the coverage and efficiency of field irrigation systems.}
\resumeItem{ Developed an intuitive device discovery system integrated with a mobile app, simplifying network setup and management for end users.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/luancsl/TaxiCarSimulator}{\textbf{TaxiCar Simulator}} $|$ \emph{React, Google Maps, D3.js, Uber H3}}{}
\resumeItemListStart
\resumeItem{Developed a simulator to optimize driver-passenger matching using complex geospatial algorithms.}
\resumeItem{Implemented and evaluated several matching methods, including the Hexagonal Hierarchical Geospatial Indexing System (Uber H3). The simulator allowed comparative analysis of efficiency in real scenarios, considering multiple positioning variables on the map.}
\resumeItemListEnd

\resumeSubHeadingListEnd